\section{Next steps and changes}
\subsection{Ensuring project readiness and work processes}
To ensure our application will be released on time we will attempt to do Test Driven Development or TDD for short. This methodology is a part of the Agile process (and a fundamental part of the Extreme programming (XP) paradigm).
Although our ambitions will not go as far as to adhere strictly to some formal Agile process, we want to use the red-green-refactor paradigm to both practice creating unit tests and hopefully keep our codebase as bug free as possible.\\

Another process we will be utilizing from the Agile process is daily standup meetings. These meetings should be an outlier for what each team member is working on for the day, if there are any blockers or issues for the tasks and if any team members requires assistance from the rest of the group. \\

The group will be using Asana to keep track of tasks and the project status.\\

We have split the initial responsibility into 3 main categories. Models and the data layer, Services and business logic layer, and finally the views and user facing layer. Our group decided that one member is responsible for the work done inside these layers and the fourth members is responsible for integration of the layers and the overall application cohesion. \\

\subsection{Work hours expectations}
As this course is mimicking a real world team of programmers inside some company, we set our working hours to be 08:00 - 16:00 and attendance to RU is highly encouraged but as a diverse team with varying responsibilities in our private lives these working hours are very flexible.\\

\subsection{Changes}
There is some functionality we had a hard time getting fitting into our prototype. Our idea for how buyer and sellers set up hand-off at some neutral location based on geographic data. The idea was the seller sets up a radius that we could display on a map and the buyer could pick any location there to meet with the buyer.\\

After our user testing, we became aware of some features that would likely benefit our application. One user asked about where the money goes after they accepted a bid and an idea of adding a virtual wallet to our site emerged. This would be a feature that we could add after our basic functionality is met.
